The Chemistry Development Kit (CDK): atom typing, rendering, molecular formulas, and substructure searching

### 2016-09-07 article.tex
Update info Miquel
Updated the title to remove the '3'. Not uncommon in series of papers, but in the context of software versions easily confused with the release version (closes #35)

\title{The Chemistry Development Kit (CDK). 3. Atom typing, Rendering, Molecular Formula, and Substructure Searching}

@@

\author[
   addressref={um},                                 % ORCID: 0000-0001-7542-0286
   %corref={aff1},
   %noteref={n1},
   email={egon.willighagen@maastrichtuniversity.nl}
]{\inits{ELW}\fnm{Egon L} \snm{Willighagen}}
\author[
   addressref={aff2},
   email={john@nextmovesoftware.com}
]{\inits{JWM}\fnm{John W} \snm{May}}
\author[
   addressref={uppsala},
   email={jonathan.alvarsson@farmbio.uu.se}
]{\inits{JA}\fnm{Jonathan} \snm{Alvarsson}}
\author[
   addressref={uppsala},
   email={berg.arvid@gmail.com}
]{\inits{AB}\fnm{Arvid} \snm{Berg}}
\author[
   addressref={jena},
   email={kai.duehrkop@uni-jena.de}
]{\inits{KD}\fnm{Kai} \snm{Dührkop}}
\author[
   addressref={idea},
   email={jeliazkova.nina@gmail.com}
]{\inits{NJ}\fnm{Nina} \snm{Jeliazkova}}
\author[
   addressref={leicester},
   email={shk12@le.ac.uk}
]{\inits{SK}\fnm{Stefan} \snm{Kuhn}}
\author[
   addressref={wi_mit},
   email={pluskal@wi.mit.edu}
]{\inits{TP}\fnm{Tomáš}~\snm{Pluskal}}
\author[
   addressref={miquel},                             % ORCID: 0000-0002-4659-1446
   email={miguelrojasch@googlemail.com}
]{\inits{MRJ}\fnm{Miquel}~\snm{Rojas Chertó}}
\author[
   addressref={uppsala},
   email={ola.spjuth@farmbio.uu.se}
]{\inits{OS}\fnm{Ola} \snm{Spjuth}}
\author[
   addressref={gilleain},                           % ORCID: 0000-0002-8368-6954
   email={gilleain.torrance@gmail.com}
]{\inits{GT}\fnm{Gilleain} \snm{Torrance}}
\author[
   addressref={um},
   email={chris.evelo@maastrichtuniversity.nl}
]{\inits{CTE}\fnm{Chris T} \snm{Evelo}}
\author[
   addressref={nih},
   email={guhar@mail.nih.gov}
]{\inits{RG}\fnm{Rajarshi} \snm{Guha}}
\author[
   addressref={ebi},
   email={steinbeck@ebi.ac.uk}
]{\inits{CS}\fnm{Christoph}~\snm{Steinbeck}}

\address[id=um]{
  \orgname{Dept of Bioinformatics - BiGCaT, NUTRIM, Maastricht University}, % university, etc
  %\street{Waterloo Road},
  \postcode{NL-6200 MD},
  \city{Maastricht},
  \cny{The Netherlands}
}
\address[id=aff2]{
  %\orgname{??},
  %\street{D\"{u}sternbrooker Weg 20},
  %\postcode{24105},
  %\city{Kiel},
  \cny{UK}
}
\address[id=uppsala]{
  \orgname{Department of Pharmaceutical Biosciences, Uppsala University},
  %\street{D\"{u}sternbrooker Weg 20},
  \postcode{751 24},
  \city{Uppsala},
  \cny{Sweden}
}
\address[id=jena]{
  \orgname{Chair for Bioinformatics, Friedrich Schiller University},
  %\street{},
  \postcode{07743},
  \city{Jena},
  \cny{Germany}
}
\address[id=idea]{
  \orgname{Ideaconsult Ltd},
  \street{A. Kanchev 4},
  \postcode{1000},
  \city{Sofia},
  \cny{Bulgaria}
}
\address[id=wi_mit]{
  \orgname{Whitehead Institute for Biomedical Research}, 
  \street{9 Cambridge Center},
  \postcode{MA 02142},
  \city{Cambridge},
  \cny{USA}
}
\address[id=miquel]{
  \orgname{Química Clínica Aplicada},
  %\street{4 Hanway Place},
  %\postcode{W1T 1HD},
  \city{Amposta},
  \cny{Spain}
}
\address[id=gilleain]{
  %\orgname{Department of Informatics, University of Leicester},
  \street{4 Hanway Place},
  \postcode{W1T 1HD},
  \city{London},
  \cny{UK}
}
\address[id=nih]{
  \orgname{National Center for Advancing Translational Science},
  \street{9800 Medical Center Drive},
  \postcode{MD 20878},
  \city{Rockville},
  \cny{USA}
}
\address[id=ebi]{
  \orgname{Chemoinformatics and Metabolism team, European Bioinformatics Institute},
  %\street{A. Kanchev 4},
  %\postcode{1000},
  \city{Hinxton},
  \cny{UK}
}
\address[id=leicester]{
  \orgname{Department of Informatics, University of Leicester},
  %\street{},
  %\postcode{LE1 7RH},
  \city{Leicester},
  \cny{UK}
}

>>>>

% previous titles:
$
% The Chemistry Development Kit (CDK): an open-source Java library for Chemo- and Bioinformatics.
% Recent developments of the chemistry development kit (CDK) - an open-source java library for chemo- and bioinformatics.

\title{The Chemistry Development Kit (CDK): atom typing, rendering, molecular formulas, and substructure searching}

@@

\author[
   addressref={um},                                 % ORCID: 0000-0001-7542-0286
   %corref={aff1},
   %noteref={n1},
   email={egon.willighagen@maastrichtuniversity.nl}
]{\inits{ELW}\fnm{Egon L} \snm{Willighagen}}
\author[
   addressref={aff2},
   email={john@nextmovesoftware.com}
]{\inits{JWM}\fnm{John W} \snm{May}}
\author[
   addressref={uppsala},
   email={jonathan.alvarsson@farmbio.uu.se}
]{\inits{JA}\fnm{Jonathan} \snm{Alvarsson}}
\author[
   addressref={uppsala},
   email={berg.arvid@gmail.com}
]{\inits{AB}\fnm{Arvid} \snm{Berg}}
\author[
   addressref={jena},
   email={kai.duehrkop@uni-jena.de}
]{\inits{KD}\fnm{Kai} \snm{Dührkop}}
\author[
   addressref={idea},
   email={jeliazkova.nina@gmail.com}
]{\inits{NJ}\fnm{Nina} \snm{Jeliazkova}}
\author[
   addressref={leicester},
   email={shk12@le.ac.uk}
]{\inits{SK}\fnm{Stefan} \snm{Kuhn}}
\author[
   addressref={wi_mit},
   email={pluskal@wi.mit.edu}
]{\inits{TP}\fnm{Tomáš}~\snm{Pluskal}}
\author[
   addressref={miquel},                             % ORCID: 0000-0002-4659-1446
   email={mrojas@qca.es}
]{\inits{MRJ}\fnm{Miquel}~\snm{Rojas-Chertó}}
\author[
   addressref={uppsala},
   email={ola.spjuth@farmbio.uu.se}
]{\inits{OS}\fnm{Ola} \snm{Spjuth}}
\author[
   addressref={gilleain},                           % ORCID: 0000-0002-8368-6954
   email={gilleain.torrance@gmail.com}
]{\inits{GT}\fnm{Gilleain} \snm{Torrance}}
\author[
   addressref={um},
   email={chris.evelo@maastrichtuniversity.nl}
]{\inits{CTE}\fnm{Chris T} \snm{Evelo}}
\author[
   addressref={nih},
   email={guhar@mail.nih.gov}
]{\inits{RG}\fnm{Rajarshi} \snm{Guha}}
\author[
   addressref={ebi},
   email={steinbeck@ebi.ac.uk}
]{\inits{CS}\fnm{Christoph}~\snm{Steinbeck}}

\address[id=um]{
  \orgname{Dept of Bioinformatics - BiGCaT, NUTRIM, Maastricht University}, % university, etc
  %\street{Waterloo Road},
  \postcode{NL-6200 MD},
  \city{Maastricht},
  \cny{The Netherlands}
}
\address[id=aff2]{
  %\orgname{??},
  %\street{D\"{u}sternbrooker Weg 20},
  %\postcode{24105},
  %\city{Kiel},
  \cny{UK}
}
\address[id=uppsala]{
  \orgname{Department of Pharmaceutical Biosciences, Uppsala University},
  %\street{D\"{u}sternbrooker Weg 20},
  \postcode{751 24},
  \city{Uppsala},
  \cny{Sweden}
}
\address[id=jena]{
  \orgname{Chair for Bioinformatics, Friedrich Schiller University},
  %\street{},
  \postcode{07743},
  \city{Jena},
  \cny{Germany}
}
\address[id=idea]{
  \orgname{Ideaconsult Ltd},
  \street{A. Kanchev 4},
  \postcode{1000},
  \city{Sofia},
  \cny{Bulgaria}
}
\address[id=wi_mit]{
  \orgname{Whitehead Institute for Biomedical Research}, 
  \street{9 Cambridge Center},
  \postcode{MA 02142},
  \city{Cambridge},
  \cny{USA}
}
\address[id=miquel]{
  \orgname{Química Clínica Aplicada},
  %\street{4 Hanway Place},
  \postcode{43870},
  \city{Amposta},
  \cny{Spain}
}
\address[id=gilleain]{
  %\orgname{Department of Informatics, University of Leicester},
  \street{4 Hanway Place},
  \postcode{W1T 1HD},
  \city{London},
  \cny{UK}
}
\address[id=nih]{
  \orgname{National Center for Advancing Translational Science},
  \street{9800 Medical Center Drive},
  \postcode{MD 20878},
  \city{Rockville},
  \cny{USA}
}
\address[id=ebi]{
  \orgname{Chemoinformatics and Metabolism team, European Bioinformatics Institute},
  %\street{A. Kanchev 4},
  %\postcode{1000},
  \city{Hinxton},
  \cny{UK}
}
\address[id=leicester]{
  \orgname{Department of Informatics, University of Leicester},
  %\street{},
  %\postcode{LE1 7RH},
  \city{Leicester},
  \cny{UK}
}
